Turbulence in compact to giant HII regions

### 2022-05-27 Corr.tex
Javier changes 2022-05-27

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
    log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
 %log $\sigma$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
      log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma\pos$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
    log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
 %log $\sigma\pos$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
 log $\sigma\pos$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
      log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
      log $m$ &        log $\sigma\pos$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}
